The used heuristics were provided in course slides and can be divided into tre cateogries depending on their final purposes and goals. Here is possible to find the groups definitions and the heuristics in each of them: \\ 
\\
\textbf{Navigation:} this batch has the aim to evaluate how easy is to move across the website and how easy and intuitive is to find contents following the websites paths.
	\begin{itemize}
		\item \textbf{Interaction consistency:} do pages of the same type have the same links and interaction capability?
		\item \textbf{Group navigation:} is it easy to navigate among group members and from a group introductory page to 				group members (and the other way around)?
		\item \textbf{Structural Navigation:} is it easy to navigate among the semantic components of a Topic?
		\item \textbf{Semantic Navigation:} is it easy to navigate from a Topic to a related one?
		\item \textbf{Landmarks:} are landmarks useful to reach the key parts of the web site?
	\end{itemize}
\textbf{Contents:} focuses on the quality of information and data provided by the site regardless the way they are presented. 
	\begin{itemize}
		\item \textbf{Information Overload:} is the information in a page too much or too little and does it fit the page layout?
		\item \textbf{Quality of Contents:} do the contents of the page include the informations that the user should expect 				there? In other words, is the content consistent.
	\end{itemize}
\textbf{Layout:} stresses the visual image of the website and its effectiveness in terms of expressivity and ergonomic functions. 
	\begin{itemize}
		\item \textbf{Text Layout:} is the text readable? Is font size appropriate?
		\item \textbf{Interaction Placeholder:} are textual or visual labels of interactive elements “expressive”? i.e., do they reflect 			the meaning of the interaction and its effects? Are they consistent?
		\item \textbf{Spatial Allocation:} is the on-screen allocation of contents and visual appropriate for their relevance? Are 				“semantically related” elements close and “semantically distant” element far away?
		\item \textbf{Consistency of Page Structure:} do pages of the same type have the same lay out (same visual properties of 			each component and similar lay-out organization of the various elements?) 
	\end{itemize}
